On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-04 main.tex
Updated Section 5

There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^n$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

Let $\Phi$ be the polynomiall mapping 

@@

(\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),

@@

so that $\Phi_A^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $0$ is a regular value of $\Phi$, where then it follows that $\Delta_1 \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Delta_1$ then  

@@

\jac_{\xb}(\Phi_A) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)

@@

has full rank at all $\xb \in V(f^A)$. Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

With $i \in \{1,\hdots,n\}$, let $\Phi$ be as stated above.

@@

$\bz$ is a regular value of $\Phi$.

@@

We want to show that the system of polynomials 

@@

f(Ax),(\grad(f)\cdot A_{i+1})(Ax),\hdots, (\grad(f)\cdot A_n)(Ax)

@@

defines a radical ideal of dimension ? whose variety is smooth (we just want the Jacobian of the system to have full rank?), which holds if and only if 

@@

defines a radical ideal of dimension ? whose variety is smooth. Let $\Psi$ be the mapping

@@

    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

A_{i+1},\hdots. 

@@

\right),

@@

For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i$ rows, the matrix has full rank $n-i$.

@@

Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then 

@@

has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%

>>>>

There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $D^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.

@@

For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 

@@

\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),

@@

so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then  

@@

\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)

@@

has full rank at all $\xb \in V(f^A)~(\cap\R^n$?). Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. To obtain the result for all $i \in \{1,\hdots,n\}$, we take 
\Delta_1 = \bigcup_{i=1}^n \Xi_i 
where we can bound the degree by observing that 
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.

@@

Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.

@@

$\bz$ is a regular value of $\Phi_i$.

@@

We want to show that the Jacobian of the system of polynomials 

@@

f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)

@@

at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 

@@

at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping

@@

    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

A_{i+1},\hdots

@@

\right).

@@

For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.

@@

Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 

@@

has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
\Delta_1 := \bigcup_{i=1}^n \Xi_i,
where we have the following bound on the degree which proves the claim:
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
